%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Randy Zhu} \\ \vspace{1pt}
  \small 604-704-9500 $|$ \href{mailto:randyzhu@student.ubc.ca}{\underline{randyzhu@student.ubc.ca}} $|$
  \href{https://www.linkedin.com/in/rzhu08/}{{linkedin.com/in/rzhu08}} $|$
  \href{https://github.com/RandoNandoz}{\underline{github.com/RandoNandoz}}
\end{center}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Java, C\#, Python, C/C++, HTML/CSS, TypeScript, Racket/Scheme} \\
        \textbf{Frameworks}{: JUnit, Unity, Swing, JavaFX, Android, Flask} \\
        \textbf{Developer Tools}{: Git, Docker, Azure, CloudFlare, Linux, Interactive Disassembler, Cisco Wireless} \\
        \textbf{Libraries}{: Sympy, Numpy, Pandas, Matplotlib, MongoDB}
        }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Barista/Cashier}{Aug. 2021 -- Aug. 2022}
{Waves Coffee House}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Efficiently handled high customer volume, maintained sanitation, and resolved technical issues in a fast-paced cafe.}
\resumeItemListEnd
\resumeSubHeadingListEnd


\section{Volunteer}
\resumeSubHeadingListStart

\resumeSubheading
{Automation Developer}{Sep. 2023 -- Present}
{UBC Agroponics}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Orchestrated the deployment of farming automation web applications using Docker, accelerating the development lifecycle and improved scalablity.}
\resumeItem{Visualized and stored sensor data transmitted using MQTT into Postgres, ensuring efficent data storage.}
\resumeItem{Delivering 90\% cost savings by transitioning team from paid, proprietary software to free/open-source solutions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Collidy Road} $|$ \emph{Unity, C\#}}{July 2023}
\resumeItemListStart
\resumeItem{Lead developer for a top 10\% of submissions game jam project, a role-reversal of Crossy Road}
\resumeItem{Optimized particle FX and entity behaviour to support massive enemy count.}
\resumeItem{Collaborated with several artists and developers over multiple days to avoid work overlap and streamline work.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Decisions Bot} $|$ \emph{Discord API, MongoDB, Python, Docker, Git}}{March 2023}
\resumeItemListStart
\resumeItem{Developed a Discord bot to track applicants' admissions decisions.}
\resumeItem{Employed MongoDB to track decisions, and user calls to the bot to provide more reliable data warehousing.}
\resumeItem{Collaborated with end users to suggest features and feedback on the bot's behaviour.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{StudyBuddy} $|$ \emph{Firebase, Flask, OpenAI API, HTML, Python}}{June 2023 -- Present}
\resumeItemListStart
\resumeItem{Currently working on smart scheduling and studying tracking webapp.}
% \resumeItem{Working with OpenAI API to solve schedule constraint problems}
\resumeItem{Leveraged OpenAI API to solve schedule constraint problems, leading to smarter, better schedules.}
\resumeItem{Used Flask and Firebase to rapidly facilitate OAuth2 based authentication the end user.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Plantis} $|$ \emph{Typescript, React, Firebase, HTML}}{January 2023}
\resumeItemListStart
\resumeItem{Plant watering tracker/reminder app for nwHacks 2023}
\resumeItem{Architected solution to storing plant data into Cloud Firestore, a NoSQL database solution}
\resumeItem{Implementated authentication using Firebase}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Bestiebot} $|$ \emph{Reddit API, MongoDB, Gephi, Python}}{Sept 2022}
\resumeItemListStart
\resumeItem{Reddit bot used to track user interactions on forum to display user-focused data about each user's behaviour.}
\resumeItem{Using Gephi, a software for network analysis and visualization, displayed stunning visualizations of user data.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Discord Music Bot} $|$ \emph{Spotify API, Discord API, Lavalink, Python}}{Jan 2021}
\resumeItemListStart
\resumeItem{Music bot for Discord written for primarily pedagogical purposes to educate students.}
\resumeItem{Implemented a feature allows users to translate Spotify playlists using the Spotify API into YouTube format, allowing the bot to play users' playlists.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of British Columbia}{Vancouver, BC}
{BSc, Computer Science}{Sep. 2023 -- Present}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
